Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-16 paper/v2/paper-edited.tex
all

%% We have implemented a compiler for \sysname and evaluated it against several real-world configurations for data centers and core backbone networks. We demonstrate the \sysname compiler can scale to

@@

%several real-world configurations for data centers and core backbone

@@

%\textbf{Abstract---}
%We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
%%
%\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
%%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%%
%Our compiler automatically translates these specifications to a collection of BGP router configurations.
%% that can execute on existing commodity hardware.
%%
%We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
%%
%We use \sysname to specify and compile the configurations of real
%data center and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.

\textbf{Abstract---}
We develop \sysname, a language and a compiler to help network operators with a challenging, error-prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex, distributed protocols.
%
The language allows operators to specify their objectives naturally, using high-level constraints and ordered preferences on paths that traffic should take.
%through their network or other networks.
%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%
The compiler automatically translates these specifications to router-level BGP configurations, using a novel data structure that compactly encodes the flow of routing information along policy-compliant paths.
%It uses We introduce data structures and algorithms that
It guarantees that the compiled configurations correctly implement the specified policy under all possible combinations of failures.
%
We use \sysname for data center and backbone networks of a large cloud provider. We find that our language can effectively express their policies and, despite its strong guarantees, our compiler scales to topologies with hundreds or thousands of routers.

@@

We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies of data center and backbone networks.
% and compared these specifications with existing configurations.
We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds to thousands of routers, compiling in under 9 minutes in all cases.

@@

%% We evaluate \sysname by using it to encode policies of real backbone and data center networks.

@@

\subsection{Example 1:  The Backbone}

@@

\subsection{Example 2:  The Data Center}

 While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible. Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally. This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally. Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}. The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.

@@

However, this implementation has incorrect behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D. Per its policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are reused for other services outside of the data center). This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter. A similar problem will happen if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in data centers are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.

@@

\subsection{Example 2: The Data Center}

Our data center example network has three main concerns:
(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
(2) local services must not leak outside the data center, and
(3) aggregation must be performed on global prefixes to reduce churn
in the network.

@@

\begin{code}
\Define Ownership =
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)
     \True \Path \End(\Out)\}
\end{code}
\noindent
This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
end at router \CD{A}; traffic for \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location, which is otherwise unconstrained.
The special keyword \Out{} matches any location outside the data center network, while the keyword \In{} will match any location inside the network.

@@

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Locality =
    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
\end{code}
\noindent
%The first line states that there is no restriction (\Any)
%on how traffic must traverse the network for global prefixes.
%aside from the default restriction
%that traffic must not pass through the user's network and then loop
%back on itself.
%This means traffic for
%\CD{PG*} may be sent either from other data center routers or
%from external ASes.
This definition says that traffic for local
prefixes only follows paths that are internal to the network at each hop.
This constraint guarantees that the services remain reachable only to locations
inside the data center.

@@

%The first line states that there is no restriction on how traffic must traverse the network for global prefixes. This means traffic for $p_{g*}$ may be sent either from other routers in the datacenter, or from external ASes. The second line ensures that traffic for local prefixes never enters the network from an outside location. This  guarantees that the services remain reachable only to locations internal to the data center.

@@

The translation from FE to RIR is based on a set of rewriting rules.
The first step merges separate constraints. It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by path negation ($\Any \cap \NOT(a)$). The additional constraint $\Any$ ensures the routes are well-formed by restricting the paths to only those that go through the user's network.
%
For example, in the data center configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:

@@

\subsection{Product Graph IR}

@@

\subsection{Failure-Safety Analysis}

@@

\subsection{Aggregation-Safety Analysis}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/aggregation}
  \caption{Aggregation safety for a data center.}
  \label{fig:aggregation-safety}
  \vspace{-1em}
\end{figure}

@@

For example, recall the data center example from \S\ref{sec:motivation}, with the policy
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the simplified PGIR. Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}. This process is repeated for other aggregation locations (e.g., $Y$).

@@

We apply \sysname on real policies for backbone and data center networks. Our main goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.

@@

We obtained routing policy for the backbone network and for the data centers of a large cloud provider. Multiple data centers share this policy. The backbone network connects to the data centers and also has many external BGP neighbors. The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for data center routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).

The networks have the type of policies that we outline earlier (\S\ref{sec:motivation}). The backbone network classifies external neighbors into several different categories and prefers paths through them in order. It does not want to provide transit among certain types of neighbors. For some neighbors, it prefers some links over the others. It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA). Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.

All routers in the datacenter network run BGP using a private AS number and peer with each other and with the backbone network over eBGP. The routers aggregate prefixes when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region. They also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.

\begin{figure}
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
  \caption{Compilation time. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

@@

We found that we could translate all network policies to \sysname. We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname. The data center operator said that he found the language intuitive. The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the data center policies were correctly translated. For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.

Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the data center networks.

@@

We study the compilation of time for both policies as a function of network size. Even though the networks we study have a fixed topology and size, we can explore the impact of size because our converted policies are network-wide and the compiler takes topology itself as an input. For the data center network, we build and provide as input fat tree~\cite{fattree} topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy. We take this approach to smoothly explore different sizes.
%There is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete data center topologies. For a given size, our reported results match those for the concrete topologies.

For the backbone network, the internal topology does not matter since all routers connect in a full iBGP mesh. We explore different mesh sizes and randomly map neighboring networks to routers. Even though each border router connects to many external peers, we count only the mesh size.

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes. For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on each predicate in parallel. Note that a single predicate can describe many prefixes, for example by matching on a disjunction of prefixes. At their largest sizes, the per-predicate compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.

@@

Total compilation for the largest data center is less than 9 minutes total. Unlike the data center policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases. Compilation for the largest backbone network, takes less than 3 minutes total. The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.

In both examples, we observe that our safety analysis algorithm for finding preferences is highly efficient, taking only a small fraction of the total running time. PGIR minimization is proportionally the most expensive compilation phase, however minimization can be capped after a certain number of iterations for larger networks if necessary. Both the backbone and data center networks policies we considered can be successfully compiled without minimization.

@@

\begin{figure}[t!]
  \subcaptionbox{Data center}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
  \subcaptionbox{Backbone network}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
  \caption{Configuration minimization. \label{fig:config-min}}
  \vspace{-1em}
\end{figure}

@@

Figure~\ref{fig:config-min} shows the size of the compiled ABGP policies as a function of the topology size. The naive translation of PGIR to ABGP outlined in \S\ref{sec:compilation} generates extremely large ABGP policies by default. To offset this, the compiler performs ABGP configuration minimization both during and after the PGIR to ABGP translation phase.
%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
Minimization is highly effective for both the data center and backbone policies. In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.

%for i in *.set; do grep bgp $i | wc; done
However, even minimized configurations are hundreds or thousands of lines per router. For the backbone network, the size of \sysname configurations is roughly similar to the BGP components of actual router configurations, though qualitative differences exist (see below). We did not have actual configurations for the data center network; they are dynamically generated from templates.

@@

Finally, we comment briefly on how \sysname-generated configurations differ from configurations or templates generated by operators.
%
In some cases, \sysname configurations are similar. For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.

In other cases, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result. Some key differences that we observed were:

@@

$ii)$ operators prevented unneeded propagation of more-specific route announcements from a neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements;

@@

We are currently investigating if such differences matter to operators (e.g., if they want to read \sysname configurations) and, if necessary, how to reduce them.

@@

\paragraph*{SDN Languages}
\sysname{} was heavily influenced by recent SDN programming
languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
as well as path queries~\cite{queries}.
Each of these languages is oriented around regular expressions, which
describe paths through a network, and predicates, which classify packets.
In particular, FatTire allows programmers to define sets of paths together
with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
and the compiler will generate appropriate OpenFlow rules.
\sysname is more expressive as it allows users to specify preferences among
paths and it generates distributed implementations that tolerate any number of faults.
Because FatTire generates data plane rules up front,
specifying higher levels of fault tolerance comes
at the cost of generating additional rules that tax switch memory.
In contrast, \sysname uses traditional distributed
control plane mechanisms to react to faults, which do not impose additional memory cost.
Because of the differences in the underlying technology, the analyses
and compilation algorithms used in \sysname are quite different from
previous work on SDN.
Finally, in addition to using path-based abstractions
for intra-domain routing, \sysname uses them for inter-domain routing as
well, unlike any existing SDN language.

\paragraph*{Configuration Automation}
Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices. In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way.
However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences. Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.

\paragraph*{Configuration Analysis}
The notion that configuring network devices is difficult and error-prone is not new.
Past researchers have tried to tackle this problem by analyzing existing
firewall configurations~\cite{fang,lumeta,margrave} and
BGP configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe} and reporting errors or inconsistencies when they are detected.
Our research is complementary to these analysis
efforts.  We hope to eliminate bugs by using higher-level
languages and a ``correct-by-construction''
methodology.  By proposing network administrators write configurations
at a high-level of abstraction, a whole host of low-level errors can be avoided.

\paragraph*{Configuration Synthesis}
ConfigAssure~\cite{narain:lisa05,narain+:configassure}
is another system designed to
help users define and debug low-level router
configurations.  Inputs to
ConfigAssure include a \emph{configuration database}, which contains a
collection of tuples over constants and configuration variables, and a
\emph{requirement}, which is a set of constraints.
%For instance, the tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
%\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
%by configuration variable \texttt{int(1)} with virtual IP address
%defined by configuration variable \texttt{int(2)}.  The constraint
%\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
%contains tuples defining HSRP group identifiers and virtual IPs for
%interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
%\texttt{rexb}.
The authors use a combination of logic programming and
SAT solving to find concrete values for configuration variables.
%such as \texttt{int(1)}.
ConfigAssure handles configuration for a wide range of protocols and many
different concerns.  In contrast, the scope of \sysname is much
narrower.  In return, \sysname offers compact, higher-level
abstractions customized for our domain, such as regular paths, as well
as domain-specific analyses customized to those abstractions, such as
our failure safety analysis.  The implementation technology is also
entirely different, as we define algorithms over automata and graphs
as opposed to using logic programming and SAT-based model-finding.

>>>>

%% We have implemented a compiler for \sysname and evaluated it against several real-world configurations for datacenters and core backbone networks. We demonstrate the \sysname compiler can scale to

@@

%several real-world configurations for datacenters and core backbone

@@

%\textbf{Abstract---}
%We develop a system called \sysname to help network operators with a challenging and error prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex distributed protocols.
%%
%\sysname allows operators to specify their objectives naturally, describing high-level constraints and preferences on the types of paths that traffic should take through their network or other networks.
%%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%%
%Our compiler automatically translates these specifications to a collection of BGP router configurations.
%% that can execute on existing commodity hardware.
%%
%We introduce data structures and algorithms that guarantee that the compiled, distributed configurations correctly implement the routing policy under all possible combinations of failures.
%%
%We use \sysname to specify and compile the configurations of real
%datacenter and backbone networks.  We show that, despite its strong guarantees, it scales to topologies with hundreds to thousands of routers.

\textbf{Abstract---}
We develop \sysname, a language and a compiler to help network operators with a challenging, error-prone task: bridging the gap between network-wide routing objectives and low-level configurations of devices that run complex, distributed protocols.
%
The language allows operators to specify their objectives naturally, using high-level constraints and ordered preferences on paths that traffic should take.
%through their network or other networks.
%using ranked sets of paths which may be partial or end-to-end and may also refer to other networks.
%
The compiler automatically translates these specifications to router-level BGP configurations, using a novel data structure that compactly encodes the flow of routing information along policy-compliant paths.
%It uses We introduce data structures and algorithms that
It guarantees that the compiled configurations correctly implement the specified policy under all possible combinations of failures.
%
We use \sysname for datacenter and backbone networks of a large cloud provider. We find that our language can effectively express their policies and, despite its strong guarantees, our compiler scales to topologies with hundreds or thousands of routers.

@@

We have implemented our language and compiler in a system called \sysname. To evaluate it, we use it to specify real policies of datacenter and backbone networks.
% and compared these specifications with existing configurations.
We find that our language expresses such policies easily, and that the compiler scales to topologies with hundreds to thousands of routers, compiling in under 9 minutes in all cases.

@@

%% We evaluate \sysname by using it to encode policies of real backbone and datacenter networks.

@@

\subsection{Example 1:  The backbone}

@@

\subsection{Example 2:  The datacenter}

 While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible. Consider the datacenter network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, datacenter networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally. This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally. Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}. The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.

@@

However, this implementation has incorrect behavior in the face of failures. Suppose links X--G and X--H fail. Then, X will hear announcements for \CD{PL*} from C and D, having traversed from G and H to Y to C and D. Per its policy implementation, X will start "leaking" these prefixes externally. Depending on the rationale for local services, this leak could impact security (e.g., if the services are sensitive) or availability (e.g., if the \CD{PL*} prefixes are reused for other services outside of the datacenter). This problem does not manifest without failures because then X has and prefers paths to \CD{PL*} through G and H since they are shorter. A similar problem will happen if links Y--G and Y--H fail.
%\footnote{A different problem occurs when links X--C and X--D (or Y--C and Y--D) fail. X (Y) may stop announcing the global prefixes because they would be heard through G and H.}
Link failures in datacenters are frequent and it is not uncommon to have multiple failed links at a given time~\cite{dc-failure-study}.

@@

\subsection{Example 2: The datacenter}

Our datacenter example network has three main concerns:
(1) traffic for the prefix allocated to each top-of-rack router must be able to reach that router,
(2) local services must not leak outside the datacenter, and
(3) aggregation must be performed on global prefixes to reduce churn
in the network.

@@

\begin{code}
\Define Ownership =
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)
     \True \Path \End(\Out)\}
\end{code}
\noindent
This definition says that traffic for prefix \CD{PG1} is allowed to follow only paths that
end at router \CD{A}; traffic for \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
Any traffic destined for a prefix that not a part of the datacenter should be allowed to leave the datacenter and end at some external location, which is otherwise unconstrained.
The special keyword \Out{} matches any location outside the datacenter network, while the keyword \In{} will match any location inside the network.

@@

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Locality =
    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
\end{code}
\noindent
%The first line states that there is no restriction (\Any)
%on how traffic must traverse the network for global prefixes.
%aside from the default restriction
%that traffic must not pass through the user's network and then loop
%back on itself.
%This means traffic for
%\CD{PG*} may be sent either from other datacenter routers or
%from external ASes.
This definition says that traffic for local
prefixes only follows paths that are internal to the network at each hop.
This constraint guarantees that the services remain reachable only to locations
inside the datacenter.

@@

%The first line states that there is no restriction on how traffic must traverse the network for global prefixes. This means traffic for $p_{g*}$ may be sent either from other routers in the datacenter, or from external ASes. The second line ensures that traffic for local prefixes never enters the network from an outside location. This  guarantees that the services remain reachable only to locations internal to the datacenter.

@@

The translation from FE to RIR is based on a set of rewriting rules.
The first step merges separate constraints. It takes the cross product of per-prefix constraints, where logical conjunction ($a \AND b$) is replaced by intersection on regular constraints ($a \Intersect b$), logical disjunction is replaced by union, and logical negation ($\NOT a$) is replaced by path negation ($\Any \cap \NOT(a)$). The additional constraint $\Any$ ensures the routes are well-formed by restricting the paths to only those that go through the user's network.
%
For example, in the datacenter configuration from \S\ref{sec:propane}, combining the \CD{Locality} and \CD{Ownership} policies results in the following RIR:

@@

\subsection{Product graph IR}

@@

\subsection{Failure-safety analysis}

@@

\subsection{Aggregation-safety analysis}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/aggregation}
  \caption{Aggregation safety for a datacenter.}
  \label{fig:aggregation-safety}
  \vspace{-1em}
\end{figure}

@@

For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the simplified PGIR. Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}. This process is repeated for other aggregation locations (e.g., $Y$).

@@

We apply \sysname on real policies for backbone and datacenter networks. Our main goals are to evaluate if its language is expressive enough for real-world policies and the time the compiler takes to generate router configurations.

@@

We obtained routing policy for the backbone network and for the datacenters of a large cloud provider. Multiple datacenters share this policy. The backbone network connects to the datacenters and also has many external BGP neighbors. The high-level policies of these networks are captured in an English document which guides operators when writing configuration templates for datacenter routers or actual configurations for the backbone network (where templates are not used because the network has less regular structure).

The networks have the types of policies that we outlined earlier (\S\ref{sec:motivation}). The backbone network classifies external neighbors into several different categories and prefers paths through them in order. It does not want to provide transit among certain types of neighbors. For some neighbors, it prefers some links over the others. It supports communities based on which it will not announce certain routes externally or announce them only within a geographic region (e.g., West Coast of the USA). Finally, it has many filters, e.g., to prevent bogons (private address space) from external neighbors, prevent customers from providing transit to other large networks, prevent traversing providers through peers, etc.

Routers in the datacenter network run BGP using private AS numbers and peer with each other and with the backbone network over eBGP. The routers aggregate some prefix blocks when announcing them to the backbone network, they keep some prefixes internal, and attach communities for some other prefixes that should not traverse beyond the geographic region. The datacenter networks also have policies by which some prefixes should not be announced beyond a certain tier in the datacenter hierarchy.

\begin{figure}
  \subcaptionbox{Datacenter}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-dc.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/compilation-times-backbone.png}} \\
  \caption{Compilation time. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

@@

We found that we could translate all network policies to \sysname. We verified with the operators that our translation preserved intended semantics.\footnote{Not intended as a scientific test, but we also asked the two operators if they would find it easy to express their policies in \sysname. The datacenter operator said that he found the language intuitive. The backbone operator said that formalizing the policy in \sysname seemed equally easy or difficult as formalizing in RPSL~\cite{RFC2622}, but he appreciated that he would have to do it only once for the whole network (not per-router) and did not have to manually compute various local preferences, import-export filters, and MEDs.} We found that the datacenter policies were correctly translated. For the backbone network, the operator mentioned an additional policy that was not present in the English document, which we added later.

Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the datacenter networks.

@@

We study the compilation of time for both policies as a function of network size. Even though the networks we study have a fixed topology and size, we can explore the impact of size because the policies are network-wide and the compiler takes topology itself as an input. For the datacenter network, we build and provide as input fat tree~\cite{fattree} topologies of different sizes, assign a /24 prefix to each ToR switch, and randomly map prefixes to each type of prefix group with a distinct routing policy.
%We take this approach to smoothly explore different sizes.
%There is a parameterized way to build fat trees~\cite{fattree}, which does not exist for our concrete datacenter topologies. For a given size, our reported results match those for the concrete topologies.
For the backbone network, the internal topology does not matter since all routers connect to each other through iBGP. We explore different (full iBGP) mesh sizes and randomly map neighboring networks to routers. Even though each border router connects to many external peers, we count only the mesh size.

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
Figure~\ref{fig:compilation-times} shows the compilation times for datacenter and backbone networks of different sizes. For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on predicates in parallel. A single predicate can describe many prefixes, for example by matching on a disjunction of prefixes. At their largest sizes, the per-predicate compilation time is roughly 10 seconds for the datacenter network and 45 seconds for the backbone network.

@@

Total compilation for the largest datacenter is less than 9 minutes total. Unlike the datacenter policy, the number of prefixes for the backbone policy remains relatively fixed as the topology size increases. Compilation for the largest backbone network, takes less than 3 minutes total. The inclusion of more preferences in the backbone policy increases the size of the PGIR, which leads to PGIR construction and minimization taking proportionally more time.

In both examples, we observe that our failure-safety analysis algorithm for finding preferences is highly efficient, taking only a small fraction of the total running time. PGIR minimization is the most expensive compilation phase. If needed, minimization can be capped after a certain number of iterations for large networks. Both the backbone and datacenter  policies we considered can be successfully compiled without minimization.

@@

\begin{figure}[t!]
  \subcaptionbox{Datacenter}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-dc.png}}
  \subcaptionbox{Backbone}
    {\includegraphics[width=.49\columnwidth]{figures/config-compression-backbone.png}} \\
  \caption{Configuration minimization. \label{fig:config-min}}
  \vspace{-1em}
\end{figure}

@@

Figure~\ref{fig:config-min} shows the size of the compiled ABGP policies as a function of the topology size. The naive translation of PGIR to ABGP outlined in \S\ref{sec:compilation} generates extremely large ABGP policies by default. To offset this, the compiler performs ABGP configuration minimization both during and after the PGIR to ABGP translation phase.
%Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans.
Minimization is highly effective for both the datacenter and backbone policies. In all cases, minimized policies are a small fraction of the size of their non-minimized counterparts.

%for i in *.set; do grep bgp $i | wc; done
However, even minimized configurations are hundreds or thousands of lines per router. For the backbone network, the size of \sysname configurations is roughly similar to the BGP components of actual router configurations, though qualitative differences exist (see below). We did not have actual configurations for the datacenter network; they are dynamically generated from templates.

@@

We comment briefly on how \sysname-generated configurations differ from configurations or templates generated by operators.
%
In some ways, \sysname configurations are similar. For example, preferences among neighboring ASes are implemented with a community value to tag incoming routes according to preference, which is then used at other border routers to influence decisions.

In other ways, the \sysname configurations are different, relying on a different BGP mechanism to achieve the same result. Some key differences that we observed were:

@@

$ii)$ operators prevented unneeded propagation of more-specific route announcements from a less-preferred neighboring AS based on their out-of-band knowledge about the topology, whereas \sysname propagated these advertisements;

@@

We are investigating if such differences matter to operators, e.g., if they want to read \sysname configurations, and, if necessary, how to reduce them.

@@

Our work draws on four threads of prior work.

\para{SDN languages}
\sysname{} was heavily influenced by SDN programming
languages such as NetKAT~\cite{netkat}, Merlin~\cite{foster:merlin}, FatTire~\cite{fattire},
as well as path queries~\cite{queries}.
Each of these languages is oriented around regular expressions, which
describe paths through a network, and predicates, which classify packets.
In particular, FatTire allows programmers to define sets of paths together
with a fault tolerance level (\emph{i.e.,} tolerate 1 or 2 faults)
and the compiler generates appropriate OpenFlow rules.
\sysname is more expressive as it allows users to specify preferences among
paths, and it generates distributed implementations that tolerate any number of faults.
Because FatTire generates data plane rules up front,
specifying higher levels of fault tolerance comes
at the cost of generating additional rules that tax switch memory.
In contrast, \sysname relies on distributed
control plane mechanisms to react to faults, which do not have additional memory cost.
Because of the differences in the underlying technology, the analyses
and compilation algorithms used in \sysname are quite different from
previous work on SDN.
Finally, in addition to using path-based abstractions
for intra-domain routing, \sysname uses them for inter-domain routing as
well, unlike existing SDN languages.

\para{Configuration automation}
Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices. In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way.
However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences. Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.

\para{Configuration analysis}
The notion that configuring network devices is difficult and error-prone is not new.
In the past, researchers have tried to tackle this problem by analyzing existing
firewall configurations~\cite{fang,lumeta,margrave} and
router configurations~\cite{feamster+:rcc,feamster:thesis,ipassure,batfish,bagpipe,arc} and reporting errors or inconsistencies when they are detected.
Our research is complementary to these analysis
efforts.  We hope to eliminate bugs by using higher-level
languages and a ``correct-by-construction''
methodology.  By proposing network administrators write configurations
at a high-level of abstraction, a whole host of low-level errors can be avoided and policy implementation can be simplified.

\para{Configuration synthesis}
ConfigAssure~\cite{narain:lisa05,narain+:configassure}
is another system designed to
help users define and debug low-level router
configurations.  Inputs to
ConfigAssure include a \emph{configuration database}, which contains a
collection of tuples over constants and configuration variables, and a
\emph{requirement}, which is a set of constraints.
%For instance, the tuple \texttt{hsrp(rexa,rA1,int(1),int(2))} states that interface
%\texttt{rA1} on device \texttt{rexa} belongs to the HSRP group defined
%by configuration variable \texttt{int(1)} with virtual IP address
%defined by configuration variable \texttt{int(2)}.  The constraint
%\texttt{hsrp\_subnet([rexa-rA1,rexb-rB1])} states that a database
%contains tuples defining HSRP group identifiers and virtual IPs for
%interfaces \texttt{rA1} and \texttt{rB1} on devices \texttt{rexa} and
%\texttt{rexb}.
The authors use a combination of logic programming and
SAT solving to find concrete values for configuration variables.
%such as \texttt{int(1)}.
ConfigAssure handles configuration for a wide range of protocols and many
different concerns.  In contrast, the scope of \sysname is much
narrower.  In return, \sysname offers compact, higher-level
abstractions customized for our domain, such as regular paths, as well
as domain-specific analyses customized to those abstractions, such as
our failure safety analysis.  The implementation technology is also
entirely different, as we define algorithms over automata and graphs
as opposed to using logic programming and SAT-based model-finding.
